Supplementary Information for:

### 2017-07-11 supp/supp.Rmd
remove old scripts

```{r initialize, include=FALSE}
# Source default parameters and functions
sapply(c("R/conversions.R", "R/def_pars.R", "R/init_env.R", "R/plot_results.R",
         "R/run_coral.R", "R/run_coral_ss.R", "R/sym_PI.R", "R/run_steady_states.R", 
         "R/plot_steady_states.R", "R/sensitivity.R"), source, .GlobalEnv)
# Get default parameters
defpars <- def_pars()
```

>>>>

```{r initialize, include=FALSE}
# Source default parameters and functions
sapply(c("R/run_steady_states.R", "R/plot_steady_states.R", "R/reported_metrics.R",
         "R/sensitivity.R", "R/conversions.R"), source, .GlobalEnv)
# Get default parameters
defpars <- def_pars()
```
